Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Updated Figure 10

algo_obj_dens_clust <- fit_highd_model(
  highd_data = one_c_shaped_data, 
  nldr_data = tsne_one_c_shaped, 
  bin1 = num_bins_x_one_c_shaped, 
  q = 0.1, 
  benchmark_highdens = 5)

@@

error_mnist <- error_mnist |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()
```

@@

algo_obj_mnist <- fit_highd_model(
  highd_data = training_data_mnist, 
  nldr_data = tsne_mnist2, 
  bin1 = num_bins_x_mnist, 
  q = 0.1, 
  benchmark_highdens = 5)

>>>>

algo_obj_dens_clust <- fit_highd_model(
  highd_data = one_c_shaped_data, 
  nldr_data = tsne_one_c_shaped, 
  bin1 = num_bins_x_one_c_shaped, 
  q = 0.1, 
  benchmark_highdens = 1)

@@

error_mnist <- error_mnist |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup() |>
  mutate(method = factor(method,
                         levels = c("UMAP", "tSNE", "tSNE2", "PHATE", "TriMAP", "PaCMAP")))
```

@@

algo_obj_mnist <- fit_highd_model(
  highd_data = training_data_mnist, 
  nldr_data = tsne_mnist2, 
  bin1 = num_bins_x_mnist, 
  q = 0.1, 
  benchmark_highdens = 1)
